\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-31 appendix.qmd
Add tSNE diff perplexity values with PBMC3k data

@@

In this step, we aim to create a smoother surface in the low-dimensional space by removing long edges from the triangular mesh. This process helps eliminate outliers and noise while preserving important local relationships and intricate structures within the data. To achieve this, distances between vertices are sorted, and unique distance values are extracted. A data frame is created to calculate the differences between consecutive distance values, and the largest difference serves as a threshold to identify long edges. By removing edges that exceed this threshold, the algorithm refines the triangular mesh (see @fig-traingularmeshgr).

dist_p <- plot_dist(distance)  +
  geom_hline(yintercept = benchmark, colour = "red") + 
  ylab(expression(d^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 12))

dist_p
```

trimesh + trimesh_gr +
  plot_layout(ncol = 2)

@@

@@

>>>>

## Default parameter values

Removing all the bins that have a standard number of points less than a certain benchmark value will generate unnecessary holes within the triangular mesh. Therefore, before removing the low-density bins, it's necessary to investigate the number of points in neighboring bins as well.

The process begins by identifying the six nearest hex bins of specified low-density hex bins. To identify the nearest hex bins 2D Euclidean distance metric is used. Then, we calculate the mean density, as outlined in the equations:

### Benchmark value to remove long edges {#sec-rmlgdefault}

Determining a benchmark value for removing long edges isn't a straightforward process with standard guidelines. Having a default value provides a practical starting point for decision-making, helping users choose whether to stick with the default, choose a value below it, or select one above it for long edge removal.

To calculate the default value, the process involves computing the 2D Euclidean distances between the vertices in the triangular mesh. Initially, distances between vertices are sorted. Then, unique distance values are extracted. Following this, the differences between consecutive distance values are computed, and a data frame is constructed with unique distance values and their corresponding differences. The first largest difference is then used as a benchmark to identify and remove the long edges.

dist_p <- plot_dist(distance)  +
  geom_hline(yintercept = benchmark, colour = "blue") + 
  ylab(expression(d^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 12)) 
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Is the default benchmark value effective in removing the long edges to construct a smooth surface in 2D? (a) Triangular mesh with coloured edges by their type, (b) Distribution of 2D Euclidean distances between triangular mesh vertices."
#| label: fig-defaultrmlg
##| out-width: 100%

trimesh_gr + dist_p +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

@@

Creating a smooth surfaces in 2D involves experimenting with various benchmark values. The challenge lies in determining the most effective benchmark value. This is precisely why the default value was introduced, as outlined in @sec-rmlgdefault, serving as a fundamental reference. To assess its effectiveness, a visual inspection of the triangular mesh is conducted to verify whether it successfully eliminates long edges. If it does, proceeding with that value is a effective choice; if not, it signals the initiation of the tuning process. @fig-diffrmlg shows how the 2D triangular meshes look after removing long edges with different benchmark values. Higher values tend to retain long edges, while lower values may remove not only long edges but also shorter ones.

## To find the benchmark value
benchmark_umap_s_curve <- find_benchmark_value(.data = distance_umap_s_curve, distance_col = distance)

trimesh_umap_s_curve <- ggplot(df_bin_centroids_umap_s_curve, aes(x = x, y = y)) +
  geom_segment(data = tr_from_to_df_umap_s_curve, aes(x = x_from, y = y_from, xend = x_to, yend = y_to)) +
  geom_point(size = 2, colour = "#33a02c") +
  coord_equal()

trimesh_umap_s_curve <- trimesh_umap_s_curve +
  #ggtitle("(a)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  ) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3) 
# theme(axis.text = element_text(size = 5),
#       axis.title = element_text(size = 7))

trimesh_gr_umap_s_curve <- colour_long_edges(.data = distance_umap_s_curve, benchmark_value = benchmark_umap_s_curve, triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_gr_umap_s_curve <- trimesh_gr_umap_s_curve +
  geom_point(size = 2, colour = "#33a02c") +
  #ggtitle("(b)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  #coord_equal() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  ) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

trimesh_removed_umap_s_curve <- remove_long_edges(.data = distance_umap_s_curve, benchmark_value = benchmark_umap_s_curve,
                                                  triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_removed_umap_s_curve <- trimesh_removed_umap_s_curve +
  # xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  # theme(axis.text = element_text(size = 5),
  #       axis.title = element_text(size = 7)) +
  geom_point(colour = "#33a02c", size = 0.5) +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

trimesh_removed_umap_s_curve1 <- remove_long_edges(.data = distance_umap_s_curve, benchmark_value = 0.8794136,
                                                  triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_removed_umap_s_curve1 <- trimesh_removed_umap_s_curve1 +
  # xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  # theme(axis.text = element_text(size = 5),
  #       axis.title = element_text(size = 7)) +
  geom_point(colour = "#33a02c", size = 0.5) +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

trimesh_removed_umap_s_curve2 <- remove_long_edges(.data = distance_umap_s_curve, benchmark_value = 5.0891822,
                                                  triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_removed_umap_s_curve2 <- trimesh_removed_umap_s_curve2 +
  # xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  # theme(axis.text = element_text(size = 5),
  #       axis.title = element_text(size = 7)) +
  geom_point(colour = "#33a02c", size = 0.5) +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'c', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

@@

```{r}
#| echo: false
#| fig-cap: "What is the effective benchmark value to remove long edges? (a) benchmark value = $0.8794136$, (b) benchmark value = $1.696$ (default), and (c) benchmark value = $5.0891822$."
#| label: fig-diffrmlg
##| out-width: 100%

trimesh_removed_umap_s_curve1 + trimesh_removed_umap_s_curve + trimesh_removed_umap_s_curve2 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='bottom')
```

@@

## How model perform less than and greater than the selected number of bins (UMAP with S-curve)

### 2024-01-31 paper.qmd
Add tSNE diff perplexity values with PBMC3k data

@@

>>>>

- If it is completely a mess, then that is also further evidence that the fit is poor in high-dimensions.

@@

<!--tSNE parm 1-->

tSNE_pbmc <- read_rds("data/pbmc/pbmc_3k_festem/pbmc_tsne_5.rds")

```{r}
#| warning: false
#| echo: false
num_bins_pbmc <- calculate_effective_x_bins(.data = tSNE_pbmc, x = tSNE1,
                                            cell_area = 1) ##23

shape_value_pbmc <- calculate_effective_shape_value(.data = tSNE_pbmc,
                                                    x = tSNE1, y = tSNE2) ## 0.8772751
shape_value_pbmc <- 0.8772751

## To extract bin centroids
hexbin_data_object_pbmc <- extract_hexbin_centroids(nldr_df = tSNE_pbmc,
                                                    num_bins = num_bins_pbmc,
                                                    shape_val = shape_value_pbmc, x = tSNE1, y = tSNE2)

tSNE_pbmc_with_hb_id <- tSNE_pbmc |>
  dplyr::mutate(hb_id = hexbin_data_object_pbmc$hb_data@cID)

## To generate a data set with high-D and 2D training data
df_all_pbmc <- dplyr::bind_cols(training_data_pbmc |> dplyr::select(-ID), tSNE_pbmc_with_hb_id)

## To find the benchmark value
benchmark_pbmc <- find_benchmark_value(.data = distance_pbmc, distance_col = distance)

trimesh_removed_pbmc_tsne <- remove_long_edges(.data = distance_pbmc, benchmark_value = benchmark_pbmc,
                                               triangular_object = tr1_object_pbmc, distance_col = distance)

trimesh_removed_pbmc_tsne <- trimesh_removed_pbmc_tsne +
  geom_point(size = 2, colour = "#33a02c") +
  #ggtitle("(b)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  #coord_equal() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  )

plot_list2_pbmc_error <- error_df |>
    mutate(type = factor(type , levels = c("error 2 or less", "error 2-10", "error 10-15", "error 15-20", "error 20-25", "error 25-30", "error 30-35", "error greter than 35"))) |>
    ggplot(aes(x = tSNE1,
               y = tSNE2, color = type))+
    geom_point(alpha=0.5, size = 0.1) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#fee0d2", "#fcbba1",
                                         "#fc9272", "#fb6a4a", "#ef3b2c",
                                         "#cb181d", "#a50f15", "#99000d"))

```{r}
#| echo: false
#| fig-cap: "(a) 2D layout from tSNE (perplexity = 5) applied for the PBMC3k dataset. Is this a best representation of the original data?, (b)  Model in the 2D space with tSNE (<>)"
#| label: fig-nldervisPBMCtSNE1
#| out-width: 100%
#| fig-pos: h

#plot_list2_pbmc + 
trimesh_removed_pbmc_tsne + plot_list2_pbmc_error +
plot_layout(guides='collect', ncol=3) &
  theme(legend.position='bottom')

<!--tSNE parm 2-->

tSNE_pbmc <- read_rds("data/pbmc/pbmc_3k_festem/pbmc_tsne_2.rds")

```{r}
#| warning: false
#| echo: false
num_bins_pbmc <- calculate_effective_x_bins(.data = tSNE_pbmc, x = tSNE1,
                                            cell_area = 1) ##23

shape_value_pbmc <- calculate_effective_shape_value(.data = tSNE_pbmc,
                                                    x = tSNE1, y = tSNE2) ## 0.8772751
shape_value_pbmc <- 0.8772751

## To extract bin centroids
hexbin_data_object_pbmc <- extract_hexbin_centroids(nldr_df = tSNE_pbmc,
                                                    num_bins = num_bins_pbmc,
                                                    shape_val = shape_value_pbmc, x = tSNE1, y = tSNE2)

tSNE_pbmc_with_hb_id <- tSNE_pbmc |>
  dplyr::mutate(hb_id = hexbin_data_object_pbmc$hb_data@cID)

## To generate a data set with high-D and 2D training data
df_all_pbmc <- dplyr::bind_cols(training_data_pbmc |> dplyr::select(-ID), tSNE_pbmc_with_hb_id)

## To find the benchmark value
benchmark_pbmc <- find_benchmark_value(.data = distance_pbmc, distance_col = distance)

trimesh_removed_pbmc_tsne <- remove_long_edges(.data = distance_pbmc, benchmark_value = benchmark_pbmc,
                                               triangular_object = tr1_object_pbmc, distance_col = distance)

trimesh_removed_pbmc_tsne <- trimesh_removed_pbmc_tsne +
  geom_point(size = 2, colour = "#33a02c") +
  #ggtitle("(b)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  #coord_equal() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  )

plot_list2_pbmc_error <- error_df |>
    mutate(type = factor(type , levels = c("error 2 or less", "error 2-10", "error 10-15", "error 15-20", "error 20-25", "error 25-30", "error 30-35", "error greter than 35"))) |>
    ggplot(aes(x = tSNE1,
               y = tSNE2, color = type))+
    geom_point(alpha=0.5, size = 0.1) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#fee0d2", "#fcbba1",
                                         "#fc9272", "#fb6a4a", "#ef3b2c",
                                         "#cb181d", "#a50f15", "#99000d"))

```{r}
#| echo: false
#| fig-cap: "(a) 2D layout from tSNE (perplexity = 2) applied for the PBMC3k dataset. Is this a best representation of the original data?, (b)  Model in the 2D space with tSNE (<>)"
#| label: fig-nldervisPBMCtSNE2
#| out-width: 100%
#| fig-pos: h

#plot_list2_pbmc + 
trimesh_removed_pbmc_tsne + plot_list2_pbmc_error +
plot_layout(guides='collect', ncol=3) &
  theme(legend.position='bottom')

### 2024-01-31 paper.tex
Add tSNE diff perplexity values with PBMC3k data

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\item
  Intro to the data set (This data set contains 13,714 features across
  2,700 samples within a single assay. The active assay is RNA, with
  13,714 features representing different gene expressions.)
\item
  2622 cells
\item
  Evaluate Festem on DEG detection (Festem enabled identification of
  often-missed fine cell types)
\item
  Using the Festem-selected genes, identified 10 clusters in the PBMCsk
  data and annotated them based on the expression of canonical markers
\item
  The 10 clusters included immune cells such as naive CD4 T cells,
  memory CD4 T cells, CD8 T cells, CD14 monocytes, FCGR3A monocytes,
  Natural Killer (NK) cells, B cells and Dendritic Cells (DC).
\item
  In addition to these common cell types, Festem identified a fine cell
  type, CD27− CD4+ memory T cells, which were often missed by other
  methods.
\item
  The CD27. CD4+ memory T cells identified by Festem expressed common
  marker genes (IL7R and S100A4) of memory T cells, but did not express
  CD27. These cells also had downregulated expression of SELL, CCR7, MAL
  and LEF1, and upregulated expression of CCL5 (Fig. 4B) and thus were
  the CD27- CD4+ memory T cells in the literature (36). The CD27- CD4+
  memory T cells were known to be at a more differentiated state and
  have stronger antigen-recall responses than their CD27+ counterparts.
\item
  15 PCs
\item
  Num bins along the x-axis = 23, shape parameter = 0.8772751
\item
  learned from the model: There are 3 well-separated clusters in 2D, but
  if look at the model in high-D space, the three clusters are much
  closer. Also, there is some continuity within the clustering structure
  and it didn't capture well. Therefore UMAP with n:neighbour 30 is not
  a good representation for this data set.
\item
  The most important parameter is n\_neighbors - the number of
  approximate nearest neighbors used to construct the initial
  high-dimensional graph. It effectively controls how UMAP balances
  local versus global structure - low values will push UMAP to focus
  more on local structure by constraining the number of neighboring
  points considered when analyzing the data in high dimensions, while
  high values will push UMAP towards representing the big-picture
  structure while losing fine detail.
\item
  The second parameter we'll investigate is min\_dist, or the minimum
  distance between points in low-dimensional space. This parameter
  controls how tightly UMAP clumps points together, with low values
  leading to more tightly packed embeddings. Larger values of min\_dist
  will make UMAP pack points together more loosely, focusing instead on
  the preservation of the broad topological structure.
\item
  The third parameter is metric. This parameter plays a crucial role in
  determining how distances are computed within the ambient space of the
  input data (The term ``ambient space'' refers to the original or
  initial space in which the data exists before any transformation or
  dimensionality reduction).
\end{itemize}

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\item
  Intro to the data set (This data set contains 13,714 features across
  2,700 samples within a single assay. The active assay is RNA, with
  13,714 features representing different gene expressions.)
\item
  2622 cells
\item
  Evaluate Festem on DEG detection (Festem enabled identification of
  often-missed fine cell types)
\item
  Using the Festem-selected genes, identified 10 clusters in the PBMCsk
  data and annotated them based on the expression of canonical markers
\item
  The 10 clusters included immune cells such as naive CD4 T cells,
  memory CD4 T cells, CD8 T cells, CD14 monocytes, FCGR3A monocytes,
  Natural Killer (NK) cells, B cells and Dendritic Cells (DC).
\item
  In addition to these common cell types, Festem identified a fine cell
  type, CD27− CD4+ memory T cells, which were often missed by other
  methods.
\item
  The CD27. CD4+ memory T cells identified by Festem expressed common
  marker genes (IL7R and S100A4) of memory T cells, but did not express
  CD27. These cells also had downregulated expression of SELL, CCR7, MAL
  and LEF1, and upregulated expression of CCL5 (Fig. 4B) and thus were
  the CD27- CD4+ memory T cells in the literature (36). The CD27- CD4+
  memory T cells were known to be at a more differentiated state and
  have stronger antigen-recall responses than their CD27+ counterparts.
\item
  15 PCs
\item
  Num bins along the x-axis = 23, shape parameter = 0.8772751
\item
  learned from the model: There are 3 well-separated clusters in 2D, but
  if look at the model in high-D space, the three clusters are much
  closer. Also, there is some continuity within the clustering structure
  and it didn't capture well. Therefore UMAP with n:neighbour 30 is not
  a good representation for this data set.
\item
  The most important parameter is n\_neighbors - the number of
  approximate nearest neighbors used to construct the initial
  high-dimensional graph. It effectively controls how UMAP balances
  local versus global structure - low values will push UMAP to focus
  more on local structure by constraining the number of neighboring
  points considered when analyzing the data in high dimensions, while
  high values will push UMAP towards representing the big-picture
  structure while losing fine detail.
\item
  The second parameter we'll investigate is min\_dist, or the minimum
  distance between points in low-dimensional space. This parameter
  controls how tightly UMAP clumps points together, with low values
  leading to more tightly packed embeddings. Larger values of min\_dist
  will make UMAP pack points together more loosely, focusing instead on
  the preservation of the broad topological structure.
\item
  The third parameter is metric. This parameter plays a crucial role in
  determining how distances are computed within the ambient space of the
  input data (The term ``ambient space'' refers to the original or
  initial space in which the data exists before any transformation or
  dimensionality reduction).
\item
  If it is completely a mess, then that is also further evidence that
  the fit is poor in high-dimensions.
\end{itemize}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-nldervisPBMCtSNE1-1.pdf}

\caption{\label{fig-nldervisPBMCtSNE1}(a) 2D layout from tSNE
(perplexity = 5) applied for the PBMC3k dataset. Is this a best
representation of the original data?, (b) Model in the 2D space with
tSNE (\textless\textgreater)}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-nldervisPBMCtSNE2-1.pdf}

\caption{\label{fig-nldervisPBMCtSNE2}(a) 2D layout from tSNE
(perplexity = 2) applied for the PBMC3k dataset. Is this a best
representation of the original data?, (b) Model in the 2D space with
tSNE (\textless\textgreater)}
